---
title: "Netflix Title Data"
author: "Esther, Megan, Cynthia"
date: "11/5/2020"
output: html_document
---

```{r include=FALSE}
source("../Group-Project/scripts/aggregatetable.R")
```

## Summary:

This is our report about Netflix Title Data. We are researching the overall 
topic of movies; what movies are popular, how many movies are released in a 
give year, how different movie streaming platforms differ, etc. This data 
set specifically covers movies that were added to  Netflix from 2014 to 
2019. The data set includes the following columns: Show ID, Type, Title, 
Director, Cast, County, Date Added, Release Year, Rating, Duration, Listed 
Genre, and a Description. We used a collection of these variables to perform
our summary calculations. 

# Summary information function
The most recent title added to Netflix is The Bling Ring. The average duration 
of movies on Netflix is 99.10082 minutes. The year with the most released titles
was 2018. The most common T.V. show rating on Netflix is TV-MA. There are 2222
Netflix titles categorized under Dramas, and there are 668 titles listed under
Documentaries.

# Aggregate Table
```{r aggregate_table, echo = FALSE}
library(knitr)
kable(by_year, caption = "Netflix Data")
```

The most pertinent observations from the aggregate table is that the number of 
TV shows and movies clearly increase in the early 2000's, and the number of 
movies increases at a higher rate than TV shows other than 1925, 1963, 2019, and 
2020. 

# Purposes of each chart



Chart 1
```{r chart1, echo = FALSE}
each_year <- netflix_titles %>%
  mutate(type_media = if_else(type == "Movie", 1, 0)) %>%
  group_by(release_year) %>%
  summarise(
    number_released_in_year = n(),
    num_movies = sum(type_media),
    num_tvshows = number_released_in_year - num_movies,
    movie_tvshow_difference = num_movies - num_tvshows
  ) %>%
  select(release_year, num_movies, num_tvshows) %>%
  gather(key = type_media, value = number_released_in_year,
         -release_year)

ggplot(data = each_year) +
  geom_col(
    mapping = aes(x = release_year, y = number_released_in_year,
                  fill = type_media),
    ) +
  labs(x= "Movie Release Year", y = "Amount of Movies and TV Shows Released",
     title = "Netflix Movie Release Year vs Amount Released", 
     fill = "Type")
```


This chart is a stacked bar chart that compares the number of movies and TV shows 
released onto Netflix per year. A similar observation can be made as the 
aggregate table, that there were more movies made than TV shows in the 2000's.
There is also a exponential increase in the number of movies and TV 
shows in the 2000's.


Chart 2
```{r chart2, echo = FALSE}
library(ggplot2)
library(RColorBrewer)

ggplot(netflix_titles, aes(x = factor(type))) +
  geom_bar(width = 0.5, fill = "skyblue1") +
  geom_text(aes(label = ..count..), stat = "count", vjust = 1.5, colour = "white") +
  labs(title = "Movies Vs TV Shows on Netflix")

```


This chart compares the number of TV Shows and Movies that were added to Netflix
from 2009 to 2014. The graph clearly depicts the drastic difference in totals
for each category, with a significantly larger amount of movies added than TV
shows. In fact, there were two times the number of Movies compared to TV shows. 


Chart 3
```{r chart3, echo = FALSE}
library(ggplot2)
netflix_titles <- netflix_titles %>%
  mutate(duration_nums = sub(" min", "", netflix_titles$duration))
netflix_titles$duration_nums = strtoi(netflix_titles$duration_nums)

movie_lengths <- netflix_titles %>% 
  filter(type == "Movie") %>% 
  select(release_year, duration_nums)


ggplot(data = movie_lengths) +
  geom_point(mapping = aes(x = release_year, y = duration_nums), 
             alpha = 0.3) +
  labs(x= "Movie Release Year", y = "Movie Duration (minutes)",
       title = "Netflix Movie Duration vs. Release Year")
```




This is a scatterplot that displays the duration of movies versus the release year.
Each point represents a movie on Netflix, From 1940 to 1960, we can see that there is a clear
upward trend in movie duration, and after 1960, the plot appears to level out, with most
movies lasting between 50 to 200 minutes. The density of the points also show that many more
movies were created in the 2000s, and the number of movies released each year continues to increase.